Real Time Adaptive Shape Reconstruction for Asteroid Landing

### 2018-11-04 manuscript.tex
Add todo
Add another todo
Correct typo
Add new material from dissertation

\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, \href{skulumani@gwu.edu}{mailto:skulumani@gwu.edu}}
and
Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{tylee@gwu.edu}{mailto:tylee@gwu.edu}}}
\affil{Goerge Washington University, Washington, DC, 20052}

@@

In this section, we demonstrate the use of the incremental shape reconstruction algorithm.
The approach is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
We utilize radar shape models of asteroids \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\).
The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.

@@

\paragraph{Asteroid 52760 Reconstruction}

@@

% \paragraph{Castalia Landing Site Selection}

% With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
% Based on the shape estimate we seek to determine the best location to land. 
% In reality, any landing site selection would be based on a wide variety of factors and constraints, however we highlight a few which can be determined autonomously and from the shape estimate.
% The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
% Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}%
%     \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
%     \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
% \end{figure}

% The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
% We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
% Landing sites which are closer will be considered preferentially over those at a larger distance.
% \Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
% The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
%     \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
%     \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
% \end{figure}
% We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
% The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
%     \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
% \end{figure}
% After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.

% \paragraph{Castalia Landing Site Refinement}
% One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
% This detail provides a much higher fidelity data source than ground based measurements. 
% In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
% However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
% The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
% As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
% \Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
%     \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
%     \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
% \end{figure}

% The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
% \Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the shape reconstruction algorithm that the small features are effectively estimated.
% \begin{figure}[htbp]
%     \centering
%     \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
%     \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
%     \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
% \end{figure}

>>>>

% TODO Think about adding current affiliation as a note, need to ask company
\author{Shankar Kulumani \footnote{PhD, Mechanical and Aerospace Engineering, \href{skulumani@gwu.edu}{mailto:skulumani@gwu.edu}}
and
Taeyoung Lee \footnote{Associate Professor, Mechanical and Aerospace Engineering, \href{tylee@gwu.edu}{mailto:tylee@gwu.edu}}}
\affil{George Washington University, Washington, DC, 20052}

@@

% TODO Add more plots from dissertation. All the uncertainty and volume plots
% TODO Show examples with the other asteroids
% TODO Mention that the software to do this is available online?
In this section, we demonstrate the use of the incremental shape reconstruction algorithm.
The approach is used to iteratively reconstruct the shape of several asteroid given LIDAR measurements.
We utilize radar shape models of asteroids \num{4769} Castalia and (\num{52760}) \num{1998} \(\text{ML}_{14}\).
The examples demonstrate the full dynamic simulation of a rigid spacecraft with an autonomous closed loop control scheme to both reconstruct the asteroid shape.

@@

\subsection{Shape Reconstruction}\label{sec:kinematic_exploration}

The results in this section utilize a kinematics only model of the spacecraft and dynamics instead of the full dynamic simulation. 
We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction.
\Cref{tab:kinematic_asteroids} lists the true shape model parameters of asteroids Geographos and Golevka.
\begin{table}[htbp]
    \centering
    \begin{tabular}{lccc}
        \toprule
        Asteroid & Semi-major axes (\si{\kilo\meter}) & Vertices & Faces\\
        \midrule
        \num{1620} Geographos & \( 2.5 \times 1.0 \times 1.05 \) & \num{8192} & \num{16380}  \\
        \num{6489} Golevka & \( 0.53 \times 0.53 \times 0.53 \)  & \num{2048} & \num{4092} \\
        \bottomrule
    \end{tabular} 
    \caption{Asteroid properties for kinematic only exploration~\label{tab:kinematic_asteroids}}
\end{table}
The spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
\Gls{lidar} measurements are generated until the total uncertainty
\begin{align*}
    \sum_i w_i,
\end{align*}
is sufficiently small.
In addition, we compute the volume of the estimate shape throughout the simulation using the algorithm presented in~\cref{sec:polyhedron_volume}.

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:geographos_partial_0}}{\includegraphics[trim={20cm 15cm 20cm 15cm}, clip,width=0.5\textwidth,keepaspectratio]{figures/computational_geometry/mesh_update/geographos/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:geographos_partial_25}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_1872.jpg}}

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:geographos_partial_50}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_3745.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:geographos_partial_75}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_5617.jpg}}

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:geographos_partial_100}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/partial_7489.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:geographos_truth}}{\includegraphics[trim={20cm 15cm 20cm 15cm},clip,keepaspectratio,width=0.5\textwidth]{figures/computational_geometry/mesh_update/geographos/truth.jpg}}
    \caption[Asteroid Geographos incremental reconstruction]{Incremental reconstruction of asteroid Geographos~\label{fig:geographos_reconstruction}}
\end{figure}

\num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
\Cref{fig:geographos_reconstruction} shows the shape reconstruction for asteroid Geographos at several distinct points during the process.
Comparing~\cref{fig:geographos_partial_100,fig:geographos_truth} shows that the final shape closely matches the true radar model.
In~\cref{fig:geographos_metrics} we display the vertex uncertainty and mesh volume as a function of time.
The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.

\begin{figure}[htbp]
    \centering
    \input{tikz/geographos_metrics.tikz}
    \caption{Normalized uncertainty and volume percent error for Geographos\label{fig:geographos_metrics}}
\end{figure}

\num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
Comparing~\cref{fig:golevka_partial_100,fig:golevka_truth} shows that the final shape closely matches the true radar model.
In~\cref{fig:golevka_metrics} we display the vertex uncertainty and mesh volume as a function of time.

\begin{figure}[htbp]
    \centering
    \input{tikz/golevka_metrics.tikz}
    \caption{Normalized uncertainty and volume percent error for Golevka\label{fig:golevka_metrics}}
\end{figure}

The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.
It is interesting to note that the reconstruction of Golevka achieves an accurate shape reconstruction in a much smaller amount of time as compared to Geographos.
This is primarily due to the smaller size of Golevka and the relatively spherical shape of the body in contrast to the highly elliptical shape of Geographos.

\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_1321.jpg}}\\%

    \subcaptionbox{\SI{50}{\percent} of measurements added\label{fig:golevka_partial_50}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_2643.jpg}}%
    \subcaptionbox{\SI{75}{\percent} of measurements added\label{fig:golevka_partial_75}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_3964.jpg}}\\%

    \subcaptionbox{\SI{100}{\percent} of measurements added\label{fig:golevka_partial_100}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/partial_5285.jpg}}%
    \subcaptionbox{True Shape Model\label{fig:golevka_truth}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,height=0.25\textheight]{figures/computational_geometry/mesh_update/golevka/truth.jpg}}
    \caption[Asteroid Golevka incremental reconstruction]{Incremental reconstruction of asteroid Golevka~\label{fig:golevka_reconstruction}}
\end{figure}
\paragraph{Asteroid 52760 Reconstruction}

@@

\paragraph{Castalia Landing Site Selection}

With an appropriate shape estimate, the spacecraft can autonomously transition from a shape reconstruction to a landing mode.
Based on the shape estimate we seek to determine the best location to land. 
In reality, any landing site selection would be based on a wide variety of factors and constraints, however we highlight a few which can be determined autonomously and from the shape estimate.
The first metric is related to the surface slope which is computed using the completed shape estimate and~\cref{eq:surface_slope}.
Areas which violate the slope constraint of \( \phi < \SI{5}{\degree} \) are excluded from further consideration.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Surface slope of Castalia\label{fig:surface_slope_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/slope.pdf}}%
    \subcaptionbox{Masked surface slope with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_slope_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/slope_masked.pdf}}
    \caption{Surface slope of asteroid Castalia\label{fig:surface_slope_castalia_both}}
\end{figure}

The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
Landing sites which are closer will be considered preferentially over those at a larger distance.
\Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
    \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
\end{figure}
We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
    \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
\end{figure}
After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.

\paragraph{Castalia Landing Site Refinement}
One key benefit of an in-situ spacecraft is the ability to measure surface features at a much higher resolution than is possible from the ground. 
This detail provides a much higher fidelity data source than ground based measurements. 
In order to emulate this in the simulation we augment the shape model of Castalia with several small craters and outcroppings as shown in~\cref{fig:castalia_refinement}.
However, these small features would be difficult to capture with the current low resolution shape model of approximately \num{4000} faces.
The lower number of faces is useful for the evaluation of the polyhedron potential model, it is not ideal for the capture of minute surface features. 
As a result, we utilize the isotropic remeshing operation described previously to selectively increase the fidelity in the region about the desired landing site.
\Cref{fig:castalia_refine_density} shows that the vertex density increases by approximately an order of magnitude in region immediately surround the landing site.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Original vertex density of the initial shape estimate\label{fig:intial_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/density.pdf}}%
    \subcaptionbox{Vertex density after refinement  around landing site\label{fig:refine_vertex_density}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/land/density.pdf}}
    \caption{Vertex density before and after refinement at asteroid Castalia\label{fig:castalia_refine_density}}
\end{figure}

The increased number of faces and vertices in the landing area allows for the capture of the small surface features.
\Cref{fig:castalia_refinement} shows that given LIDAR measurements alone and the shape reconstruction algorithm that the small features are effectively estimated.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Augmented shape of Castalia with surface features\label{fig:orig_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_true.jpg}}%
    \subcaptionbox{Estimated shape model after measuring the surface\label{fig:bump_castalia}}{\includegraphics[trim={15cm 0 15cm 0},clip,keepaspectratio,height=0.2\textheight,width=0.5\textwidth]{figures/dynamic_exploration/castalia_bump_est.jpg}}
    \caption{Asteroid Castalia with augmented with additional surface features~\label{fig:castalia_refinement}}
\end{figure}
